Minimal trap spaces of Logical models are maximal siphons of their Petri net encoding

### 2022-05-10 cmsb22.tex
Details
Updated .bnet files when available

\begin{table}[!htb]
  \caption{Timing comparisons between the proposed method and PyBoolNet on selected models from the literature.
    Columns "\(n\)" denotes the numbers of nodes of each model. Column "\(|M|\)" denotes the number of minimal trap spaces and for each method is given the computation time in seconds.
    "DNF" means that the method did not finish the computation (with a maximum of 1000 trap spaces) within the timeout of 2 minutes.}
  \centering
  \label{tab:selected_redone}
  \begin{tabular}{lrrrrrr}
    \toprule
    model & $n$ & $|M|$ & PyBoolNet (s) & Trappist (s) \\ \midrule
    CASCADE3 & 183 & 1 & 82.86 & 12.83\\
    KYNURENINE-PATHWAY & 150 & 1000+ & 74.71 & 4.22\\
    SN5 & 2746 & ??? & DNF & DNF\\
    ERBB-RECEPTOR-SIGNALING & 247 & 1000+ & DNF & 9.27\\
    Executable\_file\_for\_cholocystokinin\_model & 404 & 1000+ & 1.55 & 3.57\\
    korkut\_2015a & 99 & 1000+ & DNF & 3.06\\
    SIGNALING-PATHWAY-FOR-BUTANOL-PRODUCTION & 66 & 1000+ & 0.43 & 0.66\\
    Corral\_ThIL17diff\_15jan2021 & 92 & 1000+ & DNF & 0.91\\
    HIV-1 & 138 & 1000+ & DNF & 3.25\\
    Executable\_file\_for\_CaSQ\_derived\_mast\_cell\_activation\_model & 80 & 1000+ & 0.49 & 0.56\\
    Colitis\_associated\_colon\_cancer & 70 & 10 & 0.15 & 0.22\\
    INTERFERON-1 & 121 & 1000+ & 7.69 & 1.05\\
    TLGLSurvival & 61 & 318 & 0.59 & 0.48\\
    cho\_2016\_all\_pos & 200 & 1000+ & DNF & 3.00\\
    turei\_2016 & 4691 & ??? & DNF & DNF\\
    Human\_network & 1953 & 1000+ & DNF & DNF\\
    Executable\_file\_for\_CaSQ\_derived\_MAPK\_model & 182 & 1000+ & 75.32 & 2.26\\
    TCR-TLR5-SIGNALING-2018 & 130 & 48 & 0.93 & 0.53\\
    Hernandez\_TcellCheckPoints\_13april2020 & 218 & 1000+ & 36.21 & 2.27\\
    IMMUNE-SYSTEM & 164 & 1000+ & DNF & 2.78\\
    HMOX1-PATHWAY & 145 & 1000+ & 3.89 & 0.95\\
    Signaling\_in\_Macrophage\_Activation & 321 & 1000+ & 11.51 & 3.27\\
    FIBROBLASTS & 139 & 1000+ & DNF & 1.91\\
    S1\_Table & 1659 & 1000+ & DNF & DNF\\
    Regan2020\_Adhesion\_CIP\_Migration\_CellCycle\_Apoptosis & 121 & 78 & 40.59 & 2.15\\
    SIGNALING-IN-PROSTATE-CANCER & 133 & 1000+ & DNF & 1.70\\
    InflammatoryBowelDisease & 47 & 1 & DNF & 118.78\\
    Influenza\_A\_Virus\_Replication\_Cycle & 131 & 1000+ & 47.69 & 0.87\\
    IL\_6\_Signalling & 86 & 1000+ & 1.10 & 0.46\\
    VIRUS-REPLICATION-CYCLE & 154 & 1000+ & DNF & 1.16\\
    Executable\_file\_for\_Alzheimer\_model & 1169 & 1000+ & DNF & 6.15\\
    ER-STRESS & 182 & 1000+ & 16.15 & 0.93\\
    RA\_apoptosis\_executable\_module & 180 & 1000+ & DNF & 0.96\\
    \bottomrule
  \end{tabular}
\end{table}

>>>>

\begin{table}[!htb]
  \caption{Timing comparisons between the proposed method and PyBoolNet on selected models from the literature.
    Column "\(n\)" denotes the numbers of nodes of each model. Column "\(|M|\)" denotes the number of minimal trap spaces and for each method is given the computation time in seconds.
    "DNF" means that the method did not finish the computation (with a maximum of 1000 trap spaces) within the timeout of 2 minutes.}
  \centering
  \label{tab:selected_redone}
  \begin{tabular}{lrrrrrr}
    \toprule
    model & $n$ & $|M|$ & PyBoolNet (s) & Trappist (s) \\ \midrule
    CASCADE3 & 183 & 1 & 82.86 & 12.83\\
    KYNURENINE-PATHWAY & 150 & 1000+ & 74.71 & 4.22\\
    SN5 & 2746 & ??? & DNF & DNF\\
    ERBB-RECEPTOR-SIGNALING & 247 & 1000+ & DNF & 9.27\\
    Executable\_file\_for\_cholocystokinin\_model & 383 & 1000+ & 1.55 & 3.57\\
    korkut\_2015a & 99 & 1000+ & DNF & 3.06\\
    SIGNALING-PATHWAY-FOR-BUTANOL-PRODUCTION & 66 & 1000+ & 0.43 & 0.66\\
    Corral\_ThIL17diff\_15jan2021 & 92 & 1000+ & DNF & 0.91\\
    HIV-1 & 138 & 1000+ & DNF & 3.25\\
    Executable\_file\_for\_CaSQ\_derived\_mast\_cell\_activation\_model & 73 & 1000+ & 0.49 & 0.56\\
    Colitis\_associated\_colon\_cancer & 70 & 10 & 0.15 & 0.22\\
    INTERFERON-1 & 121 & 1000+ & 7.69 & 1.05\\
    TLGLSurvival & 61 & 318 & 0.59 & 0.48\\
    cho\_2016\_all\_pos & 200 & 1000+ & DNF & 3.00\\
    turei\_2016 & 4691 & ??? & DNF & DNF\\
    Human\_network & 1953 & 1000+ & DNF & DNF\\
    Executable\_file\_for\_CaSQ\_derived\_MAPK\_model & 181 & 1000+ & 75.32 & 2.26\\
    TCR-TLR5-SIGNALING-2018 & 130 & 48 & 0.93 & 0.53\\
    Hernandez\_TcellCheckPoints\_13april2020 & 218 & 1000+ & 36.21 & 2.27\\
    IMMUNE-SYSTEM & 164 & 1000+ & DNF & 2.78\\
    HMOX1-PATHWAY & 145 & 1000+ & 3.89 & 0.95\\
    Signaling\_in\_Macrophage\_Activation & 321 & 1000+ & 11.51 & 3.27\\
    FIBROBLASTS & 139 & 1000+ & DNF & 1.91\\
    S1\_Table & 1659 & 1000+ & DNF & DNF\\
    Regan2020\_Adhesion\_CIP\_Migration\_CellCycle\_Apoptosis & 121 & 78 & 40.59 & 2.15\\
    SIGNALING-IN-PROSTATE-CANCER & 133 & 1000+ & DNF & 1.70\\
    InflammatoryBowelDisease & 47 & 1 & DNF & 118.78\\
    Influenza\_A\_Virus\_Replication\_Cycle & 131 & 1000+ & 47.69 & 0.87\\
    IL\_6\_Signalling & 86 & 1000+ & 1.10 & 0.46\\
    VIRUS-REPLICATION-CYCLE & 154 & 1000+ & DNF & 1.16\\
    Executable\_file\_for\_Alzheimer\_model & 762 & 1000+ & DNF & 6.15\\
    ER-STRESS & 182 & 1000+ & 16.15 & 0.93\\
    RA\_apoptosis\_executable\_module & 180 & 1000+ & DNF & 0.96\\
    \bottomrule
  \end{tabular}
\end{table}
